Query Optimization for Dynamic Imputation

### 2017-05-09 paper/algorithm.tex
paper: remove input section in "query planning"

\subsection{Query planning}
\label{sec:planning}
The input to our query planner is a tuple $(T, F, J, P, G, A)$:
\begin{itemize}
\item A set of tables $T$.
\item A relation $F: T \times \Phi$ between tables and filter predicates.
\item A relation $J : T \times \Psi \times T$ between tables and join predicates.
\item A set of projection attributes $P$.
\item An optional set of grouping attributes $G$ and aggregator function $A$.
\end{itemize}

The query planner must select a join ordering in addition to placing imputation operators as described in~\Cref{sec:placement}.

@@

\subsubsection{Planning algorithm}
The planner (\Cref{algo:top-level-planner}, with helper functions in \Cref{algo:plan-helpers}) operates as follows.
First, it collects the set of attributes which are used by the operators in the plan or which are visible in the output of the plan (\Cref{lst:line:attr-start}--\Cref{lst:line:attr-end}).
This set will be used to determine which attributes are imputed.
Then, it constructs a plan cache. For each table used in the query, any available selections are pushed to the leaves and
a search over imputation operations produces various possible plans, which are added to the cache (\Cref{lst:line:sel}). If no selections are available, a 
simple scan is added to the plan cache (\Cref{lst:line:scan}). Join order is jointly optimized with imputation placements and a set of
plans encompassing all necessary tables is produced (\Cref{lst:line:join}). This set is now extended for any necessary grouping and aggregation
operations (\Cref{lst:line:group}). After a similar step has been taken for projections, the planner now contains the plan frontier (i.e.\ the
best possible set from which to pick our final plan). The final step in the planner is to find all plans that are
$\alpha$-bound and return the one that has the lowest runtime: the $\alpha$-bound optimal plan.

>>>>

\subsection{Query planning}
\label{sec:planning}
The query planner must select a join ordering in addition to placing imputation operators as described in~\Cref{sec:placement}.

@@

\subsubsection{Planning algorithm}
The planner (\Cref{algo:top-level-planner}) operates as follows.
First, it collects the set of attributes which are used by the operators in the plan or which are visible in the output of the plan (\Cref{lst:line:attr-start}--\Cref{lst:line:attr-end}).
This set will be used to determine which attributes are imputed.
Then, it constructs a plan cache. For each table used in the query, any available selections are pushed to the leaves and
a search over imputation operations produces various possible plans, which are added to the cache (\Cref{lst:line:sel}). If no selections are available, a 
simple scan is added to the plan cache (\Cref{lst:line:scan}). Join order is jointly optimized with imputation placements and a set of
plans encompassing all necessary tables is produced (\Cref{lst:line:join}). This set is now extended for any necessary grouping and aggregation
operations (\Cref{lst:line:group}). After a similar step has been taken for projections, the planner now contains the plan frontier (i.e.\ the
best possible set from which to pick our final plan). The final step in the planner is to find all plans that are
$\alpha$-bound and return the one that has the lowest runtime: the $\alpha$-bound optimal plan.
